TGI-spinal-power

### 2022-05-12 analysis/tgispine_hypotheses.Rmd
simulating models with new data

## Simulate results for one participant
```{r}
simulate_subj <- function(subid, llim, ulim) {
trialN = 10
conditionN = 8
ratingN = 3
df <- data.frame(matrix(ncol = 0, nrow = trialN*conditionN*ratingN))
df$id <- rep(subid,trialN*conditionN*ratingN)
df$trialn <- rep(1:trialN,conditionN*ratingN)
df$dermatome <- rep(rep(c(rep("within",trialN*2), rep("across",trialN*2)),2),ratingN)
df$cold_location <- rep(rep(c(rep("dist_rostr",trialN), rep("prox_caud", trialN)),conditionN/2),ratingN)
df$stimuli <- rep(c(rep("tgi",trialN*conditionN/2), rep("non-tgi",trialN*conditionN/2)),ratingN)
df$quality <- c(rep("cold",trialN*conditionN), rep("warm",trialN*conditionN), rep("burn",trialN*conditionN))

@@

# running inferential stats on simulated data - to gain idea of effect size

```{r}
library(ez)
library(psychReport)
# isolate just TGI for purposes of determining effect size
df_tgi <- df_subj[df_subj$stimuli == 'tgi' ,]

# burning VAS
burn_anova <- ezANOVA(
  data = df_tgi[df_tgi$quality == 'burn' ,]
  , dv = .(x)
  , wid = .(id)
  , within = .(dermatome, cold_location),
  return_aov = TRUE,
  detailed = TRUE
)

# warm VAS
warm_anova <- ezANOVA(
  data = df_tgi[df_tgi$quality == 'warm' ,]
  , dv = .(x)
  , wid = .(id)
  , within = .(dermatome, cold_location),
  return_aov = TRUE,
  detailed = TRUE
)

# cold VAS
cold_anova <- ezANOVA(
  data = df_tgi[df_tgi$quality == 'cold' ,]
  , dv = .(x)
  , wid = .(id)
  , within = .(dermatome, cold_location),
  return_aov = TRUE,
  detailed = TRUE
)

## t-test
# create seperate data-frames to allow for comparison
within <- df_subj[df_subj$dermatome=='within' ,]
across <- df_subj[df_subj$dermatome=='across' ,]
proxc <- within[within$cold_location== 'prox_caud' ,]
distc <- within[within$cold_location=='dist_rostr' ,]
caudc <- across[across$cold_location=='prox_caud' ,]
rostc <- across[across$cold_location=='dist_rostr' ,]

## H1
names(within)[7] <- 'within'
names(across)[7] <- 'across'
# merge
H1_df <- merge(within, across, by = c('id','cold_location','stimuli','quality'))
# difference
H1_df$diff <- H1_df$within - H1_df$across
# ttest
H1test <- t.test(H1_df$within, H1_df$across, alternative = 'two.sided', paired = TRUE)
# effect size
H1es <- (mean(H1_df$diff))/(sd(H1_df$diff))
H1test
H1es

>>>>

## Simulate results for one participant
```{r}
simulate_subj <- function(subid, llim, ulim) {
trialN = 12
conditionN = 8
ratingN = 3
df <- data.frame(matrix(ncol = 0, nrow = trialN*conditionN*ratingN))
df$id <- rep(subid,trialN*conditionN*ratingN)
df$trialn <- rep(1:trialN,conditionN*ratingN)
df$dermatome <- rep(rep(c(rep("within",trialN*2), rep("across",trialN*2)),2),ratingN)
df$cold_location <- rep(rep(c(rep("dist_rostr",trialN), rep("prox_caud", trialN)),conditionN/2),ratingN)
df$stimuli <- rep(c(rep("tgi",trialN*conditionN/2), rep("non-tgi",trialN*conditionN/2)),ratingN)
df$quality <- c(rep("cold",trialN*conditionN), rep("warm",trialN*conditionN), rep("burn",trialN*conditionN))

@@

# run ZOIB regression on the simulated data - and extract power from chosen effect sizes

```{r}
# cold ratings
model.cold = glmmTMB::glmmTMB(rating ~ stimuli + dermatome + cold_location + trialn +
                                (1|id),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+stimuli,
                      data = df30[df30$quality == 'cold' ,],
                      na.action = na.omit)
# warm ratings
model.warm = glmmTMB::glmmTMB(rating ~ stimuli + dermatome + cold_location + trialn +
                                (1|id),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+stimuli,
                      data = df30[df30$quality == 'warm' ,],
                      na.action = na.omit)

# model summaries
summary(model.cold)
summary(model.warm)

### 2022-05-12 analysis/tgispine_lme_power.Rmd
simulating models with new data

# reshape data so that there is one rating column per participant, with a VAS column = type of rating
df_VAS <- melt(df, measure.vars= c("VAScold", "VASwarm","VASburning"), 
                        id.vars=c("ID","trial_n","manipulation","procedure",
                                  "trial_type","arm","condition","cold_location"),
             variable.name = 'VAS', value.name = 'rating')
# rename the VAS ratings
df_VAS <- df_VAS %>% 
  mutate(VAS = revalue(VAS, c("VAScold" = "cold",
                                    "VASwarm" = "warm",
                                    "VASburning" = "burning")))

@@

# Summarise data per rating, per participant
df_sum <- aggregate(rating~ID*manipulation*condition*cold_location*procedure*VAS, 
                    median, data = df_VAS)
```

@@

# power analysis - using smallest effect size
fixef(model.cold.ex)[['cond']][['cold_locationprox_caud']] <- .2
pwr.cold <- powerSim(model.cold.ex)
print(pwr.cold)

>>>>

# reshape data so that there is one rating column per participant, with a VAS column = type of rating
df_VAS <- melt(df, measure.vars= c("VAScold", "VASwarm","VASburn"), 
                        id.vars=c("ID","trial_n","manipulation","order",
                                  "trial_type","arm","condition","cold_location"),
             variable.name = 'VAS', value.name = 'rating')
# rename the VAS ratings
df_VAS <- df_VAS %>% 
  mutate(VAS = revalue(VAS, c("VAScold" = "cold",
                                    "VASwarm" = "warm",
                                    "VASburn" = "burn")))

@@

# Summarise data per rating, per participant
df_sum <- aggregate(rating~ID*manipulation*condition*cold_location*order*VAS, 
                    median, data = df_VAS)
```

@@

# power analysis - using smallest effect size
fixef(model.cold.ex)[['cond']][['cold_locationprox_caud']] <- cold_loc_effect
pwr.cold <- powerSim(model.cold.ex)
print(pwr.cold)
